Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
intro sml ex

\begin{frame}[fragile]{SML modules: Example}
TODO
\end{frame}

@@

\begin{frame}[fragile]{ML-Like: Example}
\begin{minted}{sml}
structure XInt = struct
  type T = int
  val v = 3
  val f = negate
end
structure XBool = struct
  type T = bool
  val v = true
  val f = not
end
structure X =
  if flip() then XInt else XBool
signature XType = sig
  type T
  val v = T
  val f = T -> T
end
\end{minted}
\end{frame}

>>>>

\begin{frame}[fragile]{SML modules: Example}
\inputminted[fontsize=\footnotesize]{sml}{intro.sml}
\end{frame}

@@

\begin{frame}[fragile]{ML-Like: Example}
\begin{minted}{sml}
structure XInt = struct
  type T = int
  val v = 3
  val f = negate
end
structure XBool = struct
  type T = bool
  val v = true
  val f = not
end
structure X =
  if flip() then XInt else XBool
signature XType = sig
  type T
  val v: T
  val f: T -> T
end
\end{minted}
\end{frame}
